The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2010-03-04 script/en/chapters/numbertheory.tex
typo

In his paper ``Circuits for integer factorization: a proposal'' 
(\url{http://cr.yp.to/djb.html), published November 2001,
D.~J.\ Bernstein \cite{nt:Bernstein2001} addresses the problem of
factorizing large integers. Therefore, his results are of relevance from a
RSA point of view.  As a main result Bernstein claims that the
implementation of the General Number Field Sieve algorithm (GNFS)
 \index{General Number Field Sieve (GNFS)} can be improved to factor, with
the same effort as before, integers with three times more digits.

>>>>

In his paper ``Circuits for integer factorization: a proposal'' 
(\url{http://cr.yp.to/djb.html}, published November 2001,
D.~J.\ Bernstein \cite{nt:Bernstein2001} addresses the problem of
factorizing large integers. Therefore, his results are of relevance from a
RSA point of view.  As a main result Bernstein claims that the
implementation of the General Number Field Sieve algorithm (GNFS)
 \index{General Number Field Sieve (GNFS)} can be improved to factor, with
the same effort as before, integers with three times more digits.
